---
title: "Gratitude Interventions Study 2 Pairwise Analysis"
output:
  pdf_document: default
  word_document: default
  html_document: default
date: "2024-04-10"
---

#Libraries
```{r packages}

library(effsize)
library(compute.es)
library(ggsignif)
library(tidyverse)
library(psych)
library(here)

```

#Categories

```{r setup}
# specify directory
i_am("Study 2 Code/Study 2 Pairwise Analysis.Rmd")

#Set up

data <- read.csv(file = here("Study 2 Data", "Gratitude_Interventions_Study_2.csv"))

# process data
data <- data %>%
  # remove incomplete or test observations
  filter(Finished != "0", condition !="NA") %>%
  select("StartDate":"pageNo")
```

```{r measures}
data$gratitude_all <- rowMeans(data[, c("grateful", "thankful", "appreciative")], na.rm = TRUE)
mean(data$gratitude_all)
sd(data$gratitude_all)
grat_omega <- omega(data[, c("grateful", "appreciative", "thankful")])
print(grat_omega)

data$happy_all <- rowMeans(data[, c("happy", "satisfied", "content", "joyful", "pleased")], na.rm = TRUE)
mean(data$happy_all)
sd(data$happy_all)
happy_omega <- omega(data[, c("happy", "satisfied", "content", "joyful", "pleased")])
print(happy_omega)

data$optimistic_all <- rowMeans(data[, c("optimistic", "hopeful")], na.rm = TRUE)
mean(data$optimistic_all)
sd(data$optimistic_all)
optimistic_omega <- data[, c("optimistic", "hopeful")]
optimistic_omega <- omega(optimistic_omega, nfactors = 1)
print(optimistic_omega)

data$sad_all <- rowMeans(data[, c("sad", "depressed", "anxious", "nervous")], na.rm = TRUE)
mean(data$sad_all)
sd(data$sad_all)
sad_omega <- omega(data[, c("sad", "depressed", "anxious", "nervous")])
print(sad_omega)

data$indebted_all <- rowMeans(data[, c("indebted", "obligated")], na.rm = TRUE)
mean(data$indebted_all)
sd(data$indebted_all)
indebted_omega <- data[, c("indebted", "obligated")]
indebted_omega <- omega(indebted_omega, nfactors = 1)
print(indebted_omega)

mean(data$guilty)
sd(data$guilty)

data$envy_all <- rowMeans(data[, c("envious", "bitter", "jealous")], na.rm = TRUE)
mean(data$envy_all)
sd(data$envy_all)
envy_omega <- data[, c("envious", "bitter", "jealous")]
envy_omega <- omega(envy_omega, nfactors = 1)
print(envy_omega)

data$ls_total <- rowMeans(data[, c("ls_1", "ls_2", "ls_3", "ls_4", "ls_5")], na.rm = TRUE)
mean(data$ls_total)
sd(data$ls_total)
ls_omega <- data[, c("ls_1", "ls_2", "ls_3", "ls_4", "ls_5")]
ls_omega <- omega(ls_omega)
print(ls_omega)

data$sc_total <- rowMeans(data[, c("sc_1", "sc_2", "sc_3")], na.rm = TRUE)
mean(data$sc_total)
sd(data$sc_total)
sc_omega <- data[, c("sc_1", "sc_2", "sc_3")]
sc_omega <- omega(sc_omega)
print(sc_omega)

mean(data$ladder, na.rm = TRUE)
sd(data$ladder, na.rm = TRUE)

data$self_image_total <- rowMeans(data[, c("circle_task", "self_image", "signature")], na.rm = TRUE)
mean(data$self_image_total)
sd(data$self_image_total)
self_image_omega <- data[, c("circle_task", "self_image", "signature")]
self_image_omega <- omega(self_image_omega)
print(self_image_omega)

data$gratitude_3 <- -data$gratitude_3 #Reverse Code
data$gratitude_6 <- -data$gratitude_6 #Reverse Code
data$gratitude_total <- rowMeans(data[, c("gratitude_1", "gratitude_2", "gratitude_3", "gratitude_4", "gratitude_5", "gratitude_6")], na.rm = TRUE)
mean(data$gratitude_total)
sd(data$gratitude_total)
gratitude_omega <- data[, c("gratitude_1", "gratitude_2", "gratitude_3", "gratitude_4", "gratitude_5", "gratitude_6")]
gratitude_omega <- omega(gratitude_omega)
print(gratitude_omega)

data$envy_2 <- -data$envy_2 #Reverse Code
data$envy_4 <- -data$envy_5 #Reverse Code
data$envy_5 <- -data$envy_6 #Reverse Code
data$envy_6 <- -data$envy_7 #Reverse Code
data$trait_envy_total <- rowMeans(data[, c("envy_1","envy_2","envy_3","envy_5","envy_6","envy_7","envy_8","envy_9")], na.rm = TRUE)
mean(data$trait_envy_total)
sd(data$trait_envy_total)
trait_envy_omega <- data[, c("envy_1","envy_2","envy_3","envy_5","envy_6","envy_7","envy_8","envy_9")]
trait_envy_omega <- omega(trait_envy_omega)
print(trait_envy_omega)

data$pa_panas <- rowMeans(data[, c(
"panas_interested", "panas_excited", "panas_active", "panas_strong", "panas_attentive", "panas_determined", "panas_inspired", "panas_enthusiastic", "panas_proud", "panas_alert")], na.rm = TRUE)
mean(data$pa_panas)
sd(data$pa_panas)
pa_panas_omega <- data[, c(
"panas_interested", "panas_excited", "panas_active", "panas_strong", "panas_attentive", "panas_determined", "panas_inspired", "panas_enthusiastic", "panas_proud", "panas_alert")]
pa_panas_omega <- omega(pa_panas_omega)
print(pa_panas_omega)

data$na_panas <- rowMeans(data[, c(
"panas_hostile", "panas_irritable", "panas_ashamed", "panas_scared", "panas_nervous", "panas_guilty", "panas_upset", "panas_jittery", "panas_distressed", "panas_afraid")], na.rm = TRUE)
mean(data$na_panas)
sd(data$na_panas)
na_panas_omega <- data[, c(
"panas_hostile", "panas_irritable", "panas_ashamed", "panas_scared", "panas_nervous", "panas_guilty", "panas_upset", "panas_jittery", "panas_distressed", "panas_afraid")]
na_panas_omega <- omega(na_panas_omega)
print(na_panas_omega)

data$primal_belief_3 <- -data$primal_belief_3 #Reverse Code
data$primal_belief_4 <- -data$primal_belief_4 #Reverse Code
data$primal_belief_6 <- -data$primal_belief_6 #Reverse Code
data$primal_belief <- rowMeans(data[, c("primal_belief_1","primal_belief_2","primal_belief_3","primal_belief_4","primal_belief_5","primal_belief_6")], na.rm = TRUE)
mean(data$primal_belief)
sd(data$primal_belief)
primal_belief_omega <- data[, c("primal_belief_1","primal_belief_2","primal_belief_3","primal_belief_4","primal_belief_5","primal_belief_6")]
primal_belief_omega <- omega(primal_belief_omega)
print(primal_belief_omega)

```

```{r participant statistics}

data <- data %>%
  mutate(sex_name = case_when(
    sex == 1 ~ "male",
    sex == 2 ~ "female",
    sex == 3 ~ "other"
  ))

data %>%
  group_by(sex_name) %>%
  summarise(sex_count = n())

mean(data$age)
sd(data$age)

```

```{r categories}
#Conditions

control <- subset(data, condition == 1)
control_events <- subset(data, condition == 2)
control_interesting <- subset(data, condition == 3)
control_hassles <- subset(data, condition == 4)

grat_list <- subset(data, condition == 5)
grat_letter <- subset(data, condition == 6)
grat_text <- subset(data, condition == 7)
grat_hk <- subset(data, condition == 8)
grat_sing <- subset(data, condition == 9)
grat_god_list <- subset(data, condition == 10)
grat_god_letter <- subset(data, condition == 11)

```

#t-Tests (State Gratitude)

```{r measurement only (gratitude)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$gratitude_all,
  "Gratitude Letter" = grat_letter$gratitude_all,
  "Gratitude Text" = grat_text$gratitude_all,
  "Chan Gratitude List" = grat_hk$gratitude_all,
  "Mental Subtraction Task" = grat_sing$gratitude_all, 
  "Gratitude to God List" = grat_god_list$gratitude_all, 
  "Gratitude to God Letter" = grat_god_letter$gratitude_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$gratitude_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$gratitude_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (gratitude)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$gratitude_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$gratitude_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (gratitude)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$gratitude_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$gratitude_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (gratitude)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$gratitude_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$gratitude_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (gratitude)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


```{r control conditions (gratitude)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$gratitude_all,
  "Events List" = control_events$gratitude_all,
  "Interesting Events Text" = control_interesting$gratitude_all,
  "Hassles List" = control_hassles$gratitude_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```

#t-Tests (State PA)

```{r measurement only (pa)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$happy_all,
  "Gratitude Letter" = grat_letter$happy_all,
  "Gratitude Text" = grat_text$happy_all,
  "Chan Gratitude List" = grat_hk$happy_all,
  "Mental Subtraction Task" = grat_sing$happy_all, 
  "Gratitude to God List" = grat_god_list$happy_all, 
  "Gratitude to God Letter" = grat_god_letter$happy_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$happy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$happy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (pa)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$happy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$happy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (pa)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$happy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$happy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (pa)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$happy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$happy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (pa)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
```{r control conditions (pa)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$happy_all,
  "Events List" = control_events$happy_all,
  "Interesting Events Text" = control_interesting$happy_all,
  "Hassles List" = control_hassles$happy_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


#t-Tests (State Optimism)

```{r measurement only (optimism)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$optimistic_all,
  "Gratitude Letter" = grat_letter$optimistic_all,
  "Gratitude Text" = grat_text$optimistic_all,
  "Chan Gratitude List" = grat_hk$optimistic_all,
  "Mental Subtraction Task" = grat_sing$optimistic_all, 
  "Gratitude to God List" = grat_god_list$optimistic_all, 
  "Gratitude to God Letter" = grat_god_letter$optimistic_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$optimistic_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$optimistic_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (optimism)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$optimistic_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$optimistic_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (optimism)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$optimistic_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$optimistic_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (optimism)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$optimistic_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$optimistic_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (optimism)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
```{r control conditions (optimism)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$optimistic_all,
  "Events List" = control_events$optimistic_all,
  "Interesting Events Text" = control_interesting$optimistic_all,
  "Hassles List" = control_hassles$optimistic_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```




#t-Tests (State NA)
```{r measurement only (na)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$sad_all,
  "Gratitude Letter" = grat_letter$sad_all,
  "Gratitude Text" = grat_text$sad_all,
  "Chan Gratitude List" = grat_hk$sad_all,
  "Mental Subtraction Task" = grat_sing$sad_all, 
  "Gratitude to God List" = grat_god_list$sad_all, 
  "Gratitude to God Letter" = grat_god_letter$sad_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$sad_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$sad_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```

```{r events (na)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$sad_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$sad_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (na)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$sad_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$sad_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (na)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$sad_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$sad_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (na)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
```{r control conditions (na)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$sad_all,
  "Events List" = control_events$sad_all,
  "Interesting Events Text" = control_interesting$sad_all,
  "Hassles List" = control_hassles$sad_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```

#t-Tests (State Indebtedness)

```{r measurement only (indebted)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$indebted_all,
  "Gratitude Letter" = grat_letter$indebted_all,
  "Gratitude Text" = grat_text$indebted_all,
  "Chan Gratitude List" = grat_hk$indebted_all,
  "Mental Subtraction Task" = grat_sing$indebted_all, 
  "Gratitude to God List" = grat_god_list$indebted_all, 
  "Gratitude to God Letter" = grat_god_letter$indebted_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$indebted_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$indebted_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (indebted)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$indebted_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$indebted_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (indebted)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$indebted_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$indebted_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```


```{r hassles (indebted)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$indebted_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$indebted_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (indebted)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
```{r control conditions (indebted)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$indebted_all,
  "Events List" = control_events$indebted_all,
  "Interesting Events Text" = control_interesting$indebted_all,
  "Hassles List" = control_hassles$indebted_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```

#t-Tests (State Guilt)

```{r measurement only (guilt)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$guilty,
  "Gratitude Letter" = grat_letter$guilty,
  "Gratitude Text" = grat_text$guilty,
  "Chan Gratitude List" = grat_hk$guilty,
  "Mental Subtraction Task" = grat_sing$guilty, 
  "Gratitude to God List" = grat_god_list$guilty, 
  "Gratitude to God Letter" = grat_god_letter$guilty
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$guilty, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$guilty, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (guilt)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$guilty, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$guilty, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (guilt)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$guilty, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$guilty, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (guilt)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$guilty, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$guilty, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (guilt)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
```{r control conditions (guilt)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$guilty,
  "Events List" = control_events$guilty,
  "Interesting Events Text" = control_interesting$guilty,
  "Hassles List" = control_hassles$guilty
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```



#t-Tests (State Envy)

```{r measurement only (envy)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$envy_all,
  "Gratitude Letter" = grat_letter$envy_all,
  "Gratitude Text" = grat_text$envy_all,
  "Chan Gratitude List" = grat_hk$envy_all,
  "Mental Subtraction Task" = grat_sing$envy_all, 
  "Gratitude to God List" = grat_god_list$envy_all, 
  "Gratitude to God Letter" = grat_god_letter$envy_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$envy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$envy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (envy)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$envy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$envy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (envy)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$envy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$envy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (envy)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$envy_all, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$envy_all, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (envy)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
```{r control conditions (envy)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$envy_all,
  "Events List" = control_events$envy_all,
  "Interesting Events Text" = control_interesting$envy_all,
  "Hassles List" = control_hassles$envy_all
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```

#t-Tests (Life Satisfaction)

```{r measurement only (life satisfaction)}

#Create a list of datasets to compare
  grat_datasets <- list(
    "Gratitude List" = grat_list$ls_total,
    "Gratitude Letter" = grat_letter$ls_total,
    "Gratitude Text" = grat_text$ls_total,
    "Chan Gratitude List" = grat_hk$ls_total,
    "Mental Subtraction Task" = grat_sing$ls_total, 
    "Gratitude to God List" = grat_god_list$ls_total, 
    "Gratitude to God Letter" = grat_god_letter$ls_total
  )
    # Create an empty dataframe to store results
  results_df <- data.frame(Test = character(),
                           P_Value = numeric(),
                           Estimate = numeric(),
                           Statistic = numeric(),
                           Parameter = numeric(),
                           stringsAsFactors = FALSE)
  
# Loop through each dataset and perform the comparison
  for (i in seq_along(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control$ls_total, grat_datasets[[i]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control$ls_total, grat_datasets[[i]], hedges.correction = TRUE)
    
# Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
  
# Display dataframe
  print(results_df)
```
  
```{r events (life satisfaction)}

  # Create an empty dataframe to store results
  results_df <- data.frame(Test = character(),
                           P_Value = numeric(),
                           Estimate = numeric(),
                           Statistic = numeric(),
                           Parameter = numeric(),
                           stringsAsFactors = FALSE)
  
  # Loop through each dataset and perform the comparison
  for (i in seq_along(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_events$ls_total, grat_datasets[[i]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_events$ls_total, grat_datasets[[i]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste("Events List vs.", names(grat_datasets)[i]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
  
  # Display dataframe
  print(results_df)

```
```{r interesting events (life satisfaction)}
#Interesting Events

  # Create an empty dataframe to store results
  results_df <- data.frame(Test = character(),
                           P_Value = numeric(),
                           Estimate = numeric(),
                           Statistic = numeric(),
                           Parameter = numeric(),
                           stringsAsFactors = FALSE)
  
  # Loop through each dataset and perform the comparison
  for (i in seq_along(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_interesting$ls_total, grat_datasets[[i]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_interesting$ls_total, grat_datasets[[i]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
  
  # Display dataframe
  print(results_df)

```
  
```{r hassles (life satisfaction)}

  #Hassles
  
  # Create an empty dataframe to store results
  results_df <- data.frame(Test = character(),
                           P_Value = numeric(),
                           Estimate = numeric(),
                           Statistic = numeric(),
                           Parameter = numeric(),
                           stringsAsFactors = FALSE)
  
  # Loop through each dataset and perform the comparison
  for (i in seq_along(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_hassles$ls_total, grat_datasets[[i]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_hassles$ls_total, grat_datasets[[i]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste("Hassles List vs.", names(grat_datasets)[i]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
  
  # Display dataframe
  print(results_df)

```
```{r gratitude conditions (life satisfaction)}
  # Create an empty dataframe to store results
  results_df <- data.frame(Test = character(),
                           P_Value = numeric(),
                           Estimate = numeric(),
                           Statistic = numeric(),
                           Parameter = numeric(),
                           stringsAsFactors = FALSE)
  
  # Loop through each combination of datasets and perform the tests
  for (i in 1:(length(grat_datasets) - 1)) {
    for (j in (i + 1):length(grat_datasets)) {
      # Perform t-test
      t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
      # Calculate effect size
      effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
      
      # Add results to dataframe
      results_df <- rbind(results_df, data.frame(
        Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
        Statistic = t_test_result$statistic,
        Parameter = t_test_result$parameter,
        P_Value = t_test_result$p.value,
        Estimate = effect_size$estimate
      ))
    }
  }
  
  # Display dataframe
  print(results_df)

```
```{r control conditions (life satisfaction)}
  # Create a list of datasets to compare
  control_datasets <- list(
    "Measurement Only" = control$ls_total,
    "Events List" = control_events$ls_total,
    "Interesting Events Text" = control_interesting$ls_total,
    "Hassles List" = control_hassles$ls_total
  )
  
  # Create an empty dataframe to store results
  results_df <- data.frame(Test = character(),
                           P_Value = numeric(),
                           Estimate = numeric(),
                           Statistic = numeric(),
                           Parameter = numeric(),
                           stringsAsFactors = FALSE)
  
  # Loop through each combination of datasets and perform the tests
  for (i in 1:(length(control_datasets) - 1)) {
    for (j in (i + 1):length(control_datasets)) {
      # Perform t-test
      t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
      # Calculate effect size
      effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
      
      # Add results to dataframe
      results_df <- rbind(results_df, data.frame(
        Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
        Statistic = t_test_result$statistic,
        Parameter = t_test_result$parameter,
        P_Value = t_test_result$p.value,
        Estimate = effect_size$estimate
      ))
    }
  }
  
  # Display dataframe
  print(results_df)

```

#t-Tests (Social Connection)

```{r measurement only (social connection)}

#Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$sc_total,
  "Gratitude Letter" = grat_letter$sc_total,
  "Gratitude Text" = grat_text$sc_total,
  "Chan Gratitude List" = grat_hk$sc_total,
  "Mental Subtraction Task" = grat_sing$sc_total, 
  "Gratitude to God List" = grat_god_list$sc_total, 
  "Gratitude to God Letter" = grat_god_letter$sc_total
)
# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$sc_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$sc_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```

```{r events (social connection)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$sc_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$sc_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (social connection)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$sc_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$sc_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```

```{r hassles (social connection)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$sc_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$sc_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r gratitude conditions (social connection)}
# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)

```
```{r control conditions (social connection)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$sc_total,
  "Events List" = control_events$sc_total,
  "Interesting Events Text" = control_interesting$sc_total,
  "Hassles List" = control_hassles$sc_total
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)

```

#t-Tests (Ladder)

```{r measurement only (ladder)}

#Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$ladder,
  "Gratitude Letter" = grat_letter$ladder,
  "Gratitude Text" = grat_text$ladder,
  "Chan Gratitude List" = grat_hk$ladder,
  "Mental Subtraction Task" = grat_sing$ladder, 
  "Gratitude to God List" = grat_god_list$ladder, 
  "Gratitude to God Letter" = grat_god_letter$ladder
)
# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$ladder, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$ladder, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```

```{r events (ladder)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$ladder, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$ladder, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (ladder)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$ladder, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$ladder, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```

```{r hassles (ladder)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$ladder, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$ladder, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r gratitude conditions (ladder)}
# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)

```
```{r control conditions (ladder)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$ladder,
  "Events List" = control_events$ladder,
  "Interesting Events Text" = control_interesting$ladder,
  "Hassles List" = control_hassles$ladder
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)

```

#t-Tests (Self Image)

```{r measurement only (self image)}

#Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$self_image_total,
  "Gratitude Letter" = grat_letter$self_image_total,
  "Gratitude Text" = grat_text$self_image_total,
  "Chan Gratitude List" = grat_hk$self_image_total,
  "Mental Subtraction Task" = grat_sing$self_image_total, 
  "Gratitude to God List" = grat_god_list$self_image_total, 
  "Gratitude to God Letter" = grat_god_letter$self_image_total
)
# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$self_image_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$self_image_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```

```{r events (self image)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$self_image_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$self_image_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (self image)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$self_image_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$self_image_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```

```{r hassles (self image)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$self_image_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$self_image_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r gratitude conditions (self image)}
# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)

```
```{r control conditions (self image)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$self_image_total,
  "Events List" = control_events$self_image_total,
  "Interesting Events Text" = control_interesting$self_image_total,
  "Hassles List" = control_hassles$self_image_total
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)

```

#t-Tests (Trait Gratitude)

```{r measurement only (gratitude)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$gratitude_total,
  "Gratitude Letter" = grat_letter$gratitude_total,
  "Gratitude Text" = grat_text$gratitude_total,
  "Chan Gratitude List" = grat_hk$gratitude_total,
  "Mental Subtraction Task" = grat_sing$gratitude_total, 
  "Gratitude to God List" = grat_god_list$gratitude_total, 
  "Gratitude to God Letter" = grat_god_letter$gratitude_total
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$gratitude_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$gratitude_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (gratitude)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$gratitude_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$gratitude_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (gratitude)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$gratitude_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$gratitude_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (gratitude)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$gratitude_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$gratitude_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (gratitude)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


```{r control conditions (gratitude)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$gratitude_total,
  "Events List" = control_events$gratitude_total,
  "Interesting Events Text" = control_interesting$gratitude_total,
  "Hassles List" = control_hassles$gratitude_total
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
#t-Tests (Trait Envy)

```{r measurement only (trait envy)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$trait_envy_total,
  "Gratitude Letter" = grat_letter$trait_envy_total,
  "Gratitude Text" = grat_text$trait_envy_total,
  "Chan Gratitude List" = grat_hk$trait_envy_total,
  "Mental Subtraction Task" = grat_sing$trait_envy_total, 
  "Gratitude to God List" = grat_god_list$trait_envy_total, 
  "Gratitude to God Letter" = grat_god_letter$trait_envy_total
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$trait_envy_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$trait_envy_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (trait envy)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$trait_envy_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$trait_envy_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (trait envy)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$trait_envy_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$trait_envy_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (trait envy)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$trait_envy_total, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$trait_envy_total, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (trait envy)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


```{r control conditions (trait envy)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$trait_envy_total,
  "Events List" = control_events$trait_envy_total,
  "Interesting Events Text" = control_interesting$trait_envy_total,
  "Hassles List" = control_hassles$trait_envy_total
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
#t-Tests (Trait Positive Affect)

```{r measurement only (Trait Positive Affect)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$pa_panas,
  "Gratitude Letter" = grat_letter$pa_panas,
  "Gratitude Text" = grat_text$pa_panas,
  "Chan Gratitude List" = grat_hk$pa_panas,
  "Mental Subtraction Task" = grat_sing$pa_panas, 
  "Gratitude to God List" = grat_god_list$pa_panas, 
  "Gratitude to God Letter" = grat_god_letter$pa_panas
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$pa_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$pa_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (Trait Positive Affect)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$pa_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$pa_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (Trait Positive Affect)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$pa_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$pa_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (Trait Positive Affect)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$pa_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$pa_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (Trait Positive Affect)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


```{r control conditions (Trait Positive Affect)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$pa_panas,
  "Events List" = control_events$pa_panas,
  "Interesting Events Text" = control_interesting$pa_panas,
  "Hassles List" = control_hassles$pa_panas
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
#t-Tests (Trait Negative Affect)

```{r measurement only (Trait Negative Affect)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$na_panas,
  "Gratitude Letter" = grat_letter$na_panas,
  "Gratitude Text" = grat_text$na_panas,
  "Chan Gratitude List" = grat_hk$na_panas,
  "Mental Subtraction Task" = grat_sing$na_panas, 
  "Gratitude to God List" = grat_god_list$na_panas, 
  "Gratitude to God Letter" = grat_god_letter$na_panas
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$na_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$na_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (Trait Negative Affect)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$na_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$na_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (Trait Negative Affect)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$na_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$na_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (Trait Negative Affect)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$na_panas, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$na_panas, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (Trait Negative Affect)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


```{r control conditions (Trait Negative Affect)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$na_panas,
  "Events List" = control_events$na_panas,
  "Interesting Events Text" = control_interesting$na_panas,
  "Hassles List" = control_hassles$na_panas
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
#t-Tests (Primal World Beliefs)

```{r measurement only (Primal World Beliefs)}
# Create a list of datasets to compare
grat_datasets <- list(
  "Gratitude List" = grat_list$primal_belief,
  "Gratitude Letter" = grat_letter$primal_belief,
  "Gratitude Text" = grat_text$primal_belief,
  "Chan Gratitude List" = grat_hk$primal_belief,
  "Mental Subtraction Task" = grat_sing$primal_belief, 
  "Gratitude to God List" = grat_god_list$primal_belief, 
  "Gratitude to God Letter" = grat_god_letter$primal_belief
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control$primal_belief, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control$primal_belief, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Measurement Only vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r events (Primal World Beliefs)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_events$primal_belief, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_events$primal_belief, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)

```
```{r interesting events (Primal World Beliefs)}
#Interesting Events

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_interesting$primal_belief, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_interesting$primal_belief, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Interesting Events List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r hassles (Primal World Beliefs)}

#Hassles

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each dataset and perform the comparison
for (i in seq_along(grat_datasets)) {
  # Perform t-test
  t_test_result <- t.test(control_hassles$primal_belief, grat_datasets[[i]])
  # Calculate effect size
  effect_size <- effsize::cohen.d(control_hassles$primal_belief, grat_datasets[[i]], hedges.correction = TRUE)
  
  # Add results to dataframe
  results_df <- rbind(results_df, data.frame(
    Test = paste("Hassles List vs.", names(grat_datasets)[i]),
    Statistic = t_test_result$statistic,
    Parameter = t_test_result$parameter,
    P_Value = t_test_result$p.value,
    Estimate = effect_size$estimate
  ))
}

# Display dataframe
print(results_df)
```
```{r gratitude conditions (Primal World Beliefs)}

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(grat_datasets) - 1)) {
  for (j in (i + 1):length(grat_datasets)) {
    # Perform t-test
    t_test_result <- t.test(grat_datasets[[i]], grat_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(grat_datasets[[i]], grat_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(grat_datasets)[i], "vs.", names(grat_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```


```{r control conditions (Primal World Beliefs)}
# Create a list of datasets to compare
control_datasets <- list(
  "Measurement Only" = control$primal_belief,
  "Events List" = control_events$primal_belief,
  "Interesting Events Text" = control_interesting$primal_belief,
  "Hassles List" = control_hassles$primal_belief
)

# Create an empty dataframe to store results
results_df <- data.frame(Test = character(),
                         P_Value = numeric(),
                         Estimate = numeric(),
                         Statistic = numeric(),
                         Parameter = numeric(),
                         stringsAsFactors = FALSE)

# Loop through each combination of datasets and perform the tests
for (i in 1:(length(control_datasets) - 1)) {
  for (j in (i + 1):length(control_datasets)) {
    # Perform t-test
    t_test_result <- t.test(control_datasets[[i]], control_datasets[[j]])
    # Calculate effect size
    effect_size <- effsize::cohen.d(control_datasets[[i]], control_datasets[[j]], hedges.correction = TRUE)
    
    # Add results to dataframe
    results_df <- rbind(results_df, data.frame(
      Test = paste(names(control_datasets)[i], "vs.", names(control_datasets)[j]),
      Statistic = t_test_result$statistic,
      Parameter = t_test_result$parameter,
      P_Value = t_test_result$p.value,
      Estimate = effect_size$estimate
    ))
  }
}

# Display dataframe
print(results_df)
```
